MacLeish

### 2016-03-30 README.Rmd
updated README and added weather station locations

```{r, message=FALSE}
macleish <- etl("macleish")
macleish %>%
  etl_update()
```

```{r}
whately <- macleish %>%
  tbl("whately")
whately %>%
  mutate(the_year = strftime('%Y', when)) %>%
  group_by(the_year) %>%
  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(Temp_C_Avg))
orchard <- macleish %>%
  tbl("orchard")
orchard %>%
  mutate(the_year = strftime('%Y', when)) %>%
  group_by(the_year) %>%
  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(Temp_C_Avg))
```

```{r, fig.width = 7, fig.height = 5, message=FALSE}
daily <- whately %>%
  mutate(the_date = date(when)) %>%
  group_by(the_date) %>%
  summarize(N = n(), avgTemp = mean(Temp_C_Avg)) %>%
  collect()
library(ggplot2)
ggplot(data = daily, aes(x = as.Date(the_date), y = avgTemp)) +
  geom_point() + geom_smooth()
```

@@

```{r, fig.width=7, fig.height=7, message=FALSE}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addPolygons(data = macleish_layers[["boundary"]], 
              weight = 1, fillOpacity = 0.1) %>%
  addPolygons(data = macleish_layers[["buildings"]], 
              weight = 1, popup = ~ Feature) %>%
  addPolylines(data = macleish_layers[["trails"]], 
               weight = 1, color = "brown",
               popup = ~ Name) %>%
  addPolylines(data = macleish_layers[["streams"]], 
               weight = 2)
```

>>>>

```{r, message=FALSE, eval=FALSE}
macleish <- etl("macleish")
macleish %>%
  etl_update()
```

```{r, eval=FALSE}
whately <- macleish %>%
  tbl("whately")
whately %>%
  mutate(the_year = strftime('%Y', when)) %>%
  group_by(the_year) %>%
  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(Temp_C_Avg))
orchard <- macleish %>%
  tbl("orchard")
orchard %>%
  mutate(the_year = strftime('%Y', when)) %>%
  group_by(the_year) %>%
  summarize(N = n(), begin = min(when), end = max(when), avg_temp = mean(Temp_C_Avg))
```

```{r, eval=FALSE, fig.width = 7, fig.height = 5, message=FALSE}
daily <- whately %>%
  mutate(the_date = date(when)) %>%
  group_by(the_date) %>%
  summarize(N = n(), avgTemp = mean(Temp_C_Avg)) %>%
  collect()
library(ggplot2)
ggplot(data = daily, aes(x = as.Date(the_date), y = avgTemp)) +
  geom_point() + geom_smooth()
```

@@

```{r, fig.width=7, fig.height=7, message=FALSE}
library(leaflet)
leaflet() %>%
  addTiles() %>%
  addPolygons(data = macleish_layers[["boundary"]], 
              weight = 1, fillOpacity = 0.1) %>%
  addPolygons(data = macleish_layers[["buildings"]], 
              weight = 1, popup = ~ Feature) %>%
  addPolylines(data = macleish_layers[["trails"]], 
               weight = 1, color = "brown",
               popup = ~ trl_name) %>%
  addPolylines(data = macleish_layers[["streams"]], 
               weight = 2)
```
